A fast primal-dual algorithm for computing best response strategies in two-person sequential games

### 2014-07-27 paper.tex
better stopping criterion
looks much better

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
$a^Tb$: \quad \textit{the dot product of two vectors $a$ and $b$}\\
$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

\section{The proposed algorithm}
\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm
for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:pseudocode_pb}) is a use-case of
the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.

@@

Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:pseudocode_pb}, 
for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.

@@

>>>>

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $A^T$: \quad transpose of the matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: vertical stacking of the matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of the vector $v$;
\item $u^Tv$: \quad the dot product of two vectors $u$ and $v$;
\item $\mathbb{R}_+$: \quad the nonnegative part of the real-line $\mathbb{R}$;
\item $(x)_+$: \quad the component-wise maximum of the vector $x$ and 0;
\item $i_C$: \quad the indicator function of the convex set $C$;
\item $\Pi_C$: \quad the euclidean projector onto the convex set $C$;
\item $\|K\|_2$: \quad the matrix 2-norm of the matrix $K$;
\item $f^*$: \quad the Fenchel transform of the convex l.s.c function $f$;
\item \textit{l.s.c}: \quad acronyme for ``lower semi-continuous'';
\item $E^{-1}(U)$: \quad the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\end{itemize}

@@

\section{The proposed algorithm}
\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm
for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.

@@

Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:algo}, 
for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.

@@

\begin{remark}
Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:algo} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
\end{remark}

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
  \textbf{Given} Tolerance $\epsilon > 0$.\\
  \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
  \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
  \Repeat{
    $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
    \begin{eqnarray*}
      \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
      x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
      \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
  \label{Tab:algo}
\end{algorithm}
